Review of Assigned Readings

### 2018-01-03 paper/paper.tex
elaborated twitter part

\subsection{Twitter}
With the current growth of social networks, the number of global social media users reached 2.46 billion and is expected to increase to 3.02 billion by 2021 according to Statista (2018). Gabriel and Röhrs (2017) define social networks as a loose connection of people in an online or internet community respectively in a computer-based communication network (p. 12). This paper exploits the possibility to analyse shared “thoughts, views and opinions” (Stenqvist and Lönnö, 2017, p. 6) provided by such communities or communication networks.\newline
Twitter was founded in 2006 and gained rapidly worldwide popularity (Twitter 2018). and reached 330 million active users in the third quarter of 2017 (Twitter 2017, Statista 2018). As a micro-blogging platform, Twitter suits the purpose of analysing investors’ interests due to its special characteristics. In comparison to other social networks, twitter limits its posts (tweets) to relatively short messages of 140 characters. Tweets can contain observations, thoughts, links to interesting content, websites, uploaded pictures or videos. Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles.(Schmidt, 2017)

>>>>

\subsection{Twitter}
With the current growth of social networks, the number of global social media users reached 2.46 billion and is expected to increase to 3.02 billion by 2021 according to Statista (2018). Gabriel and Röhrs (2017) define social networks as a loose connection of people in an online or internet community respectively in a computer-based communication network (p. 12). This paper exploits the possibility to analyse shared “thoughts, views and opinions” (Stenqvist and Lönnö, 2017, p. 6) provided by such communities or communication networks.\\

Twitter was founded in 2006 and gained rapidly worldwide popularity (Twitter 2018). and reached 330 million active users in the third quarter of 2017 (Twitter 2017, Statista 2018). As a micro-blogging platform, Twitter suits the purpose of analysing investors’ interests due to its special characteristics. In comparison to other social networks, twitter limits its posts (tweets) to relatively short messages of 140 characters. Tweets can contain observations, thoughts, links to interesting content, websites, uploaded pictures or videos. Special conventions such as hashtags “\#” or mentions “@” are used to reference searchable content or user profiles.(Schmidt, 2017)\\

In this way, Twitter users create millions of posts that contain interests, opinions and informations in both a private and professional context.  Due to the semi-structured form, the message length restriction and classifying nature, Stenqvist and Lönnö (2017, p. 6) argue, that “Twitter has become a gold mine for opinionated data”, which is further supported in the wide adoption of researchers to analyse sentiments.\\

In relation to Bitcoin, researchers already showed that analysing investors sentiments by either using a polarity classification – classifying the language in tweets as either positive or negative (see Colianni, Rosales \& Signorotti, 2015; COMMENT SEVERIN: ADD FURTHER SOURCES) – or a lexicon based approach – attributes predefined words to specific sentiment classifications (see Stenqvist and Lönnö, 2017; COMMENT SEVERIN: ADD FURTHER SOURCES), can lead to reasonable correlations between Twitter sentiments and prices of cryptocurrencies (Stenqvist and Lönnö, 2017, p. 7). Hence, this paper focuses only on the number of daily tweets that contain the term “Bitcoin” without analysing investors interests any further than the mentioning of the term itself. This approach is based on the previous research for the stock market of Mao et al. (2015).\\
